Staged Abstract Interpreters

### 2019-03-28 paper/60_cases.tex
evaluation

We first revisit a similar technique called \textit{abstract compilation} (AC).
AC is introduced by \citet{Boucher:1996:ACN:647473.727587} as a new
implementation technique for abstract interpretation based static analysis.
The idea is inspired by partial evaluation similar to the present paper --
the program is known statically, and the interpretive overhead can be
eliminated. In AC, the compiled analysis can be represented by either text or
closures (higher-order functions). The minute difference is that the closures
can be executed immediately, while the textual programs need to be compiled and
loaded first.

>>>>

We first revisit a similar technique called \textit{abstract compilation} (AC).
AC is introduced by \citet{Boucher:1996:ACN:647473.727587} as a new
implementation technique for abstract interpretation based static analysis.
Similar to the present paper, the idea is inspired by partial evaluation:
the program is known statically and the interpretive overhead can be
eliminated. In AC, the compiled analysis can be represented by either text or
closures (higher-order functions). The minute difference is that the closures
can be executed immediately, while the textual programs need to be compiled and
loaded.
